Fractional Types

### 2019-11-19 fracGC/p.tex
simple proof that 4 toffoli is not definable

\paragraph*{Temporary Storage using Ancilla Bits.} The universality of
the Toffoli gate for classical reversible computing and of the
universality of the Toffol-Hadamard gates for quantum computing should
not distract from efficiency and safety concerns. The theorems proving
universality (i) assume that temporary storage (often called
\emph{ancilla bits}) may be used~\cite{Toffoli:1980}, and (ii) that
this temporary storage is returned to its initial state before
de-allocation. Indeed if no temporary storage is allowed, the Toffoli
gate is not universal~\cite{DBLP:conf/innovations/AaronsonGS17} and as
would be expected the more temporary storage is allowed, the more
efficient certain computations could become.

@@

By construction, the \AgdaFunction{TOFFOLI} function takes three bits,
and negates the third if the first two are both true. As
Toffoli~\cite{Toffoli:1980} demonstrated, this function is universal
for classical reversible circuits assuming it is possible to allocate
and de-allocate ancilla bits. Indeed without using ancilla bits, it is
not possible to use compositions of \AgdaFunction{TOFFOLI} functions
to implement more general versions that are controlled by more than
two bits (for example, \AgdaFunction{CTOFFOLI}). This will however be
possible in the next section once we introduce ancilla bits.

>>>>

\paragraph*{Temporary Storage using Ancilla Bits.} The universality of
the Toffoli gate for classical reversible computing and of the
universality of the Toffol-Hadamard gates for quantum computing should
not distract from efficiency and safety concerns. The theorems proving
universality (i) assume that temporary storage (often called
\emph{ancilla bits}) may be used~\cite{Toffoli:1980}, and (ii) that
this temporary storage is returned to its initial state before
de-allocation. Indeed if no temporary storage is allowed, the Toffoli
gate is not
universal~\cite{DBLP:conf/innovations/AaronsonGS17,DBLP:journals/corr/Xu15e}
and as would be expected the more temporary storage is allowed, the
more efficient certain computations could become.

@@

By construction, the \AgdaFunction{TOFFOLI} function takes three bits,
and negates the third if the first two are both true. As
Toffoli~\cite{Toffoli:1980} demonstrated, this function is universal
for classical reversible circuits assuming it is possible to allocate
and de-allocate ancilla bits. Indeed without using ancilla bits, it is
not possible to use compositions of \AgdaFunction{TOFFOLI} functions
to implement more general versions that are controlled by more than
two bits (for example, \AgdaFunction{CTOFFOLI}). The proof is simple:
the \AgdaFunction{TOFFOLI} function depends on two control bits and
possibly negates a third; when used in a circuit with four bits, the
unused bit can be either state, which means that
\AgdaFunction{TOFFOLI} generates an even permutation. The function
\AgdaFunction{CTOFFOLI} is however an odd permutation which is
unreachable from even permutations. This function will however be
definable in the next section once we introduce ancilla bits.
